Approximation as Differentiation

### 2025-06-18 main/first-order.tex
Doesn't quite make sense what I've written..

To interpret the syntactic type constructor $\synVar{L}$, we note that $\LatGal$ has a lifting monad
$\mathcal{L}$ which sends any bounded lattice $X = (X, \meet, \join, \top, \bot)$ to the lattice
$\mathcal{L}(X) = X_\bot$.

>>>>

To interpret the syntactic type constructor $\synVar{L}$, consider the strong lifting monad $\mathcal{L}$
which extends a poset $X$ with a distinguished bottom element $\bot$ and extends a monotone function $f$
between posets with a mapping from $\bot$ to $\bot$. $\mathcal{L}$ induces a strong monad $\mathcal{L}_\meet$
in any meet-semilattice on $X$. For any join-semilattice on $X$, $\mathcal{L}$ induces a costrong comonad, as
long as $X$ is bounded; the bottom element of $X$ is needed to implement the counit $\varepsilon_X:
\mathcal{L}(X) \to X$. These two in turn form a strong monad in $\LatGal$ which sends any lattice on $X$ to a
lattice on $\mathcal{L}(X)$

we note that the category of join-semilattices has a
strong monad $\mathcal{L}_{\join}$ which sends any join-semilattice $X = (X, \join, \bot)$ to the semilattice
which extends $X$ with a new bottom element $\bot_{\mathcal{L}}$ while preserving the original ordering of $X$
within the lifted structure. One can do the same for meet-semilattices, extending $X = (X, \meet, \top)$ with
a new element $\bot^*$ which also acts as the bottom element. In both cases the action on
morphisms $f$ is to map $\bot^*$ to $\bot^*$ and otherwise act as $f$:
